% ---- First-author papers ----

\item \textbf{Li J.}, Greene J.~E., Danieli S., Carlsten S.~G., Geha M., \href{https://ui.adsabs.harvard.edu/abs/2026ApJ...998L..24L}{A Possible ``Too-many-satellites'' Problem in the Isolated Dwarf Galaxy DDO 161}, \textit{ApJL} 998, L24 (2026).

\item \textbf{Li J.}, Greene J.~E., Danieli S., Carlsten S.~G., Geha M., Jiang F., Tanaka M., \href{https://ui.adsabs.harvard.edu/abs/2025arXiv250408030L}{ELVES-Dwarf I: Satellites Systems of Eight Isolated Dwarf Galaxies in the Local Volume}, \textit{ApJ} accepted, arXiv:2504.08030.

\item \textbf{Li J.}, Greene J.~E., Carlsten S.~G., Danieli S., \href{https://ui.adsabs.harvard.edu/abs/2024ApJ...975L..23L}{Hedgehog: An Isolated Quiescent Dwarf Galaxy at 2.4 Mpc}, \textit{ApJL} 975, L23 (2024).

\item \textbf{Li J.}, Melchior P., Hahn C., Huang S., \href{https://ui.adsabs.harvard.edu/abs/2024AJ....167...16L}{PopSED: Population-level Inference for Galaxy Properties from Broadband Photometry with Neural Density Estimation}, \textit{AJ} 167, 16 (2024).

\item \textbf{Li J.}, Greene J.~E., Greco J.~P., Huang S., Melchior P., Beaton R., Casey K., Danieli S., Goulding A., Joseph R., Kado-Fong E., Kim J.~H., MacArthur L.~A., \href{https://ui.adsabs.harvard.edu/abs/2023ApJ...955....1L}{Beyond Ultra-diffuse Galaxies. I. Mass-Size Outliers among the Satellites of Milky Way Analogs}, \textit{ApJ} 955, 1 (2023).

\item \textbf{Li J.}, Greene J.~E., Greco J., Beaton R., Danieli S., Goulding A., Huang S., Kado-Fong E., \href{https://ui.adsabs.harvard.edu/abs/2023ApJ...955....2L}{Beyond Ultra-diffuse Galaxies. II. Environmental Quenching of Mass-Size Outliers among the Satellites of Milky Way Analogs}, \textit{ApJ} 955, 2 (2023).

\item \textbf{Li J.}, Huang S., Leauthaud A., Moustakas J., Danieli S., Greene J.~E., Abraham R., Ardila F., Kado-Fong E., Lokhorst D., Lupton R., Price P., \href{https://ui.adsabs.harvard.edu/abs/2022MNRAS.515.5335L}{Reaching for the Edge I: probing the outskirts of massive galaxies with HSC, DECaLS, SDSS, and Dragonfly}, \textit{MNRAS} 515, 5335 (2022).

% ---- Second/third-author papers ----

\item Carlsten S., \textbf{Li J.}, Greene J., Drlica-Wagner A., Danieli S., \href{https://ui.adsabs.harvard.edu/abs/2026arXiv260216766C}{A Sample of Nearby Isolated Dwarf Galaxies: A First Look at the Mass Function of Field Dwarfs}, arXiv:2602.16766.

\item Cheng S., \textbf{Li J.}, Yang E., \href{https://ui.adsabs.harvard.edu/abs/2026ApJ...998L...6C}{Discovery of a Dwarf Planet Candidate in an Extremely Wide Orbit: 2017 OF201}, \textit{ApJL} 998, L6 (2026).

\item Carlsten S., \textbf{Li J.}, Greene J., Drlica-Wagner A., Danieli S., \href{https://ui.adsabs.harvard.edu/abs/2026arXiv260216778C}{ELVES-Field: Isolated Dwarf Galaxy Quenched Fractions Rise Below $M_* \approx 10^7$ $M_\odot$}, arXiv:2602.16778.

\item Wei L., Huang S., \textbf{Li J.}, Sun Z., Li M., Tang J., \href{https://ui.adsabs.harvard.edu/abs/2026ApJ...997...32W}{Zangetsu: A Candidate Isolated, Quiescent, and Backsplash Ultra-diffuse Galaxy in the COSMOS Field}, \textit{ApJ} 997, 32 (2026).

\item Nemer A., Hahn C., \textbf{Li J.}, Melchior P., Goodman J., \href{https://ui.adsabs.harvard.edu/abs/2024ApJ...965..157N}{Constraining Protoplanetary Disk Winds from Forbidden Line Profiles with Simulation-based Inference}, \textit{ApJ} 965, 157 (2024).

% ---- Other papers ----

\item Ma Y., Greene J.~E., Setton D.~J., Goulding A.~D. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2026ApJ..1000...59M}{Counting Little Red Dots at z < 4 with Ground-based Surveys and Spectroscopic Follow-up}, \textit{ApJ} 1000, 59 (2026).

\item Zimmerman E.~A., Gal-Yam A., Groot P.~J., Ofek E.~O. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2026arXiv260209096Z}{A Faint Progenitor System for the Faint Supernova 2024vjm}, arXiv:2602.09096.

\item Garcia A.~M., Rose J.~C., Torrey P., Caputo A. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2025arXiv251203132G}{The DREAMS Project: Disentangling the Impact of Halo-to-Halo Variance and Baryonic Feedback on Milky Way Dark Matter Density Profiles}, arXiv:2512.03132.

\item Lilie E., Rose J.~C., Lisanti M., Garcia A.~M. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2025arXiv251204157L}{The DREAMS Project: Disentangling the Impact of Halo-to-Halo Variance and Baryonic Feedback on Milky Way Dark Matter Speed Distributions}, arXiv:2512.04157.

\item Rose J.~C., Lisanti M., Torrey P., Villaescusa-Navarro F. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2025arXiv251202095R}{The DREAMS Project: Disentangling the Impact of Halo-to-Halo Variance and Baryonic Feedback on Milky Way Satellite Galaxies}, arXiv:2512.02095.

\item Pan Y., Danieli S., Greene J.~E., \textbf{Li J.}, Leauthaud A., Kado-Fong E., Luo Y., Mintz A., Brooks A., Huang S., Peter A.~H., Bhattacharyya J., Kelvin L.~S., \href{https://ui.adsabs.harvard.edu/abs/2025arXiv251212846P}{The Merian Survey: A Statistical Census of Bright Satellites of Milky Way Analogs}, arXiv:2512.12846.

\item Danieli S., Kado-Fong E., Huang S., Luo Y. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2025ApJ...993..110D}{First Data Release of the Merian Survey: A Wide-field Imaging Survey of Dwarf Galaxies at z {\ensuremath{\sim}} 0.06─0.10}, \textit{ApJ} 993, 110 (2025).

\item Luo Y., Wick J., Leauthaud A., Wetzel A. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2025arXiv251017996L}{Testing the Stellar Feedback-driven Breathing Mode in Low-mass Galaxies with Gas Kinematics}, arXiv:2510.17996.

\item Zeng Z.~C., Peter A.~H., Du X., Benson A., \textbf{Li J.}, Mace C., Yang S., \href{https://ui.adsabs.harvard.edu/abs/2025PhRvD.112f3008Z}{Diversity and universality: Evolution of dwarf galaxies with self-interacting dark matter}, \textit{Phys. Rev. D} 112, 063008 (2025).

\item Srinivasaragavan G.~P., Hamidani H., Schroeder G., Sarin N. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2025ApJ...988L..60S}{EP250108a/SN 2025kg: A Jet-driven Stellar Explosion Interacting with Circumstellar Material}, \textit{ApJL} 988, L60 (2025).

\item Mintz A., Greene J.~E., Kado-Fong E., Danieli S., \textbf{Li J.}, Luo Y., Leauthaud A., Baldassare V., Huang S., Peter A.~H., Bhattacharyya J., Li M., Pan Y., \href{https://ui.adsabs.harvard.edu/abs/2024ApJ...974..273M}{A Nonparametric Morphological Analysis of H{\ensuremath{\alpha}} Emission in Bright Dwarfs Using the Merian Survey}, \textit{ApJ} 974, 273 (2024).

\item Dou J., Peng Y., Gu Q., Renzini A. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2024ApJ...973L..23D}{The H I Reservoir in Central Spiral Galaxies and the Implied Star Formation Process}, \textit{ApJL} 973, L23 (2024).

\item Luo Y., Leauthaud A., Greene J., Huang S. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2024MNRAS.530.4988L}{The Merian survey: design, construction, and characterization of a filter set optimized to find dwarf galaxies and measure their dark matter halo properties with weak lensing}, \textit{MNRAS} 530, 4988 (2024).

\item Greene J.~E., Danieli S., Carlsten S., Beaton R. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2023ApJ...949...94G}{ELVES. III. Environmental Quenching by Milky Way-mass Hosts}, \textit{ApJ} 949, 94 (2023).

\item Keim M.~A., van Dokkum P., Danieli S., Lokhorst D., \textbf{Li J.}, Shen Z., Abraham R., Chen S., Gilhuly C., Liu Q., Merritt A., Miller T.~B., Pasha I., Polzin A., \href{https://ui.adsabs.harvard.edu/abs/2022ApJ...935..160K}{Tidal Distortions in NGC1052-DF2 and NGC1052-DF4: Independent Evidence for a Lack of Dark Matter}, \textit{ApJ} 935, 160 (2022).

\item Greene J.~E., Greco J.~P., Goulding A.~D., Huang S. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2022ApJ...933..150G}{The Nature of Low-surface-brightness Galaxies in the Hyper Suprime-Cam Survey}, \textit{ApJ} 933, 150 (2022).

\item Shi J., Peng Y., Diemer B., Stevens A.~R. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2022ApJ...927..189S}{Cold Gas in Massive Galaxies as a Critical Test of Black Hole Feedback Models}, \textit{ApJ} 927, 189 (2022).

\item Danieli S., van Dokkum P., Trujillo-Gomez S., Kruijssen J.~D. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2022ApJ...927L..28D}{NGC 5846-UDG1: A Galaxy Formed Mostly by Star Formation in Massive, Extremely Dense Clumps of Gas}, \textit{ApJL} 927, L28 (2022).

\item Liu Q., Abraham R., Gilhuly C., van Dokkum P. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2022ApJ...925..219L}{A Method to Characterize the Wide-angle Point-Spread Function of Astronomical Images}, \textit{ApJ} 925, 219 (2022).

\item Miller T.~B., van Dokkum P., Danieli S., \textbf{Li J.}, Abraham R., Conroy C., Gilhuly C., Greco J.~P., Liu Q., Lokhorst D., Merritt A., \href{https://ui.adsabs.harvard.edu/abs/2021ApJ...909...74M}{The Dragonfly Wide Field Survey. II. Accurate Total Luminosities and Colors of Nearby Massive Galaxies and Implications for the Galaxy Stellar-mass Function}, \textit{ApJ} 909, 74 (2021).

\item van Dokkum P., Lokhorst D., Danieli S., \textbf{Li J.}, Merritt A., Abraham R., Gilhuly C., Greco J.~P., Liu Q., \href{https://ui.adsabs.harvard.edu/abs/2020PASP..132g4503V}{Multi-resolution Filtering: An Empirical Method for Isolating Faint, Extended Emission in Dragonfly Data and Other Low Resolution Images}, \textit{PASP} 132, 074503 (2020).

\item Danieli S., Lokhorst D., Zhang J., Merritt A. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...894..119D}{The Dragonfly Wide Field Survey. I. Telescope, Survey Design, and Data Characterization}, \textit{ApJ} 894, 119 (2020).

% ---- Misc (abstracts, proposals, proceedings) ----

\item Han J.~J., Chiti A., Chen K., Bechtol K. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2026arXiv260221280H}{A Path to an All-Sky Survey with Roman}, white paper for the Roman Cycle 1 observation, arXiv:2602.21280.

\item \textbf{Li J.}, Greene J., Danieli S., Carlsten S., Geha M., \href{https://ui.adsabs.harvard.edu/abs/2026AAS...24714504L}{ELVES-Dwarf Survey: Probing Satellite Population of Isolated Dwarf Galaxies in the Local Volume}, AAS abstract (2026).

\item \textbf{Li J.}, Carlsten S., Danieli S., Greene J.~E., Lin X., Savino A., Telford G., \href{https://ui.adsabs.harvard.edu/abs/2025hst..prop18046L}{Testing the Mass Threshold of Reionization-Quenching with Isolated Dwarf Galaxy Hedgehog}, HST Proposal (2025).

\item Cheng S., Li J., \href{https://ui.adsabs.harvard.edu/abs/2025MPEC....K...47C}{2017 OF201}, Minor Planet Electronic Circulars (2025).

\item \textbf{Li J.}, Melchior P., Hahn C., Huang S., \href{https://ui.adsabs.harvard.edu/abs/2024AAS...24326110L}{PopSED: Population-Level Inference for Galaxy Properties from Broadband Photometry with Neural Density Estimation}, AAS abstract (2024).

\item Greene J.~E., \href{https://ui.adsabs.harvard.edu/abs/2024ngr..prop...78G}{Mapping the 3D structure of the nearby Universe with Roman+Surface Brightness Fluctuations}, NASA Roman Proposal (2024).

\item \textbf{Li J.}, \href{https://ui.adsabs.harvard.edu/abs/2023zndo...8126529L}{\texttt{smplotlib}: A Matplotlib template for SuperMongo style}, software.

\item \textbf{Li J.}, Melchior P.~M., Hahn C., Huang S., \href{https://ui.adsabs.harvard.edu/abs/2023mla..confE..20L}{Population-Level Inference for Galaxy Properties from Broadband Photometry}, ICML ML4Astro workshop (2023).

\item Han J.~J., Dey A., Price-Whelan A.~M., Najita J. et al. (including \textbf{Li J.}), \href{https://ui.adsabs.harvard.edu/abs/2023arXiv230611784H}{NANCY: Next-generation All-sky Near-infrared Community surveY}, white paper for the Roman Core Community Survey, arXiv:2306.11784.
